%\documentstyle{article}
\documentclass[a4paper,11pt,english]{article}
\usepackage{ifsym}
\usepackage[dvipdfm, hypertex]{hyperref}
\oddsidemargin=.15in
\evensidemargin=.15in
\textwidth=6in
\topmargin=-.5in
\textheight=9in
\parindent=0in
\pagestyle{empty}
%Conditional compilation statement for professional version.
\usepackage{ifthen}
\newboolean{DEBUG}
\setboolean{DEBUG}{true}

\begin{document}

\begin{center}
{\Large Jose Pablo Alberto Andreotti} \\[.5pc]
(54) 351-4730292 $\;$ albertoandreotti\verb|@|gmail.com $\;$ (54) 351-156526363 \\[3pc]
\end{center}
{\large \bf Personal Information} \\*[-.8pc]
\underline{\hspace{6in}} \\
\\
{\bf Born in Santa Cruz, Argentina}, 08/10/1982.\\
\\
{\bf Nationality}, Argentinian/Italian.\\
\\
{\bf Address}, 552, Emilio Castelar Street, C\'ordoba. Argentina.\\

{\large \bf Education} \\*[-.8pc]
\underline{\hspace{6in}} \\
\newline
{\bf Postgraduate Specialization in Distributed Systems}\\
\href{http://www.famaf.unc.edu.ar/}{Famaf}, University of C\'ordoba, 2009. \\
Average Grade: 8.87/10. \\
Final Project: High Scalable Scientific Computing using Hadoop, found \href{https://docs.google.com/viewer?a=v&pid=explorer&chrome=true&srcid=0B5AOpwg8IzVANjJlODZhZDctNWUzMS00MmNhLWI3OWMtMWNhMTdjODQwNjVl&hl=en}{here}.\\
\\
{\bf Computer Engineer}\\
Engineering Faculty, University of C\'ordoba, 2007.\\
Average Grade: 8.14/10. \\
Dissertation: Building a dual core JVM for embedded realtime systems, found \href{https://docs.google.com/viewer?a=v&pid=explorer&chrome=true&srcid=1gdJXYgQtLDHDOxGDtbKzdmAl1LmNx-yo4w6vNl-K_Z-1YocLhtJxMvoqGvd1&hl=en}{here}.\\
\\
{\bf High School at Colegio Coraz\'on de Mar\'ia}\\
Management Oriented School, 2000.\\
Average Grade: 8.22/10.\\
\\
{\bf Thesis} \\
\href{http://www.jopdesign.com}{JOP}(Java Optimizad Processor) is a hardware implementation of the JVM. My thesis 
comprises the design and implementation of a multiprocessor JVM using JOP as a building block.\\


{\large \bf Programming Experience} \\*[-.8pc]
\underline{\hspace{6in}} \\
$\triangleright$ Develpment of embedded Software in C/C++, and Java.\\
$\triangleright$ Maintenance of Linux Software in C/C++.\\
$\triangleright$ Experience on mobile platforms such as Android and iOS.\\
$\triangleright$ Test Development in Bash/Perl/Python/Java.\\
$\triangleright$ Notions of Web Services, XML, XML schema, XSLT.\\
$\triangleright$ Object Oriented Design Concepts.\\
$\triangleright$ Experience in performance optimization.\\
$\triangleright$ Experience in debbugging distributed applications.\\
$\triangleright$ Deep knowledge of computer architectures, and assembly programming.\\

\newpage
{\large \bf Other Skills} \\*[-.8pc]
\underline{\hspace{6in}} \\
$\triangleright$ Ability to lead others to achieve complex and interdependent tasks.\\
$\triangleright$ Ability to learn new technologies.\\
$\triangleright$ Software Architecture.\\
$\triangleright$ Ability to cope with change, and to rapidly accommodate to new plans, and challenges.\\
$\triangleright$ Good speaker, and with the ability to produce good quality technical documentation.\\
$\triangleright$ Results orientation.\\


{\large \bf Postgraduate Courses Attended}\\ *[-.8pc]
\underline{\hspace{6in}}
$\triangleright$ Image and video processing: From Mars to Hollywood with a stop at the hospital, Guillermo Sapiro, Duke University, first semester of 2013. Link \href{https://www.coursera.org/course/images}{here}. \\
$\triangleright$ Digital Signal Processing, Paolo Prandoni and Martin Vetterli, École Polytechnique Fédérale de Lausanne, first semester of 2013. Link \href{https://www.coursera.org/course/dsp}{here}. \\
$\triangleright$ Machine Learning\footnote{This is the online version of the course.}, Andrew Ng, Stanford University, first semester of 2012. Link \href{http://www.ml-class.org}{here}. \\
$\triangleright$ High Performance Computing: Models, Methods and Means\footnote{Unstructured Postgraduate,
and Graduate Course, Fa.M.A.F. Sincronized with Prof. Thomas Sterling's 
\href{http://www.csc.lsu.edu/Internal_review/2009/Syllabus_CSC_7600_HPC_2008.pdf}{CSC7600}.}, first semester 2010.\\
$\triangleright$ The Semantic Web, PhD Jorge Cardoso, SAP Research Germany, first semester of 2009.\\
$\triangleright$ Introduction to Radar Signal Processing, Msc Oscar Bria, 
\href{http://www.invap.net/index-e.php}{INVAP}, second semester of 2009. \href{http://postgrado.info.unlp.edu.ar/Cursos/Cursos/11-2011_Introduccion_al_Procesamiento_de_Senales_Radar.pdf}{Syllabus}.\\
$\triangleright$ Performance and Scaling in E-Commerce Systems WS, Alex Buchmann, second semester of 2008. 
\href{http://www.dvs.tu-darmstadt.de/teaching/perf/2008/}{Syllabus}.\\

{\large \bf Professional Experience}\\*[-.8pc]
\underline{\hspace{6in}}
\\
\\
\begin{tabular}{ p{2cm} l }
  {\bf Current} & {\bf Sr. Software Engineer at \href{http://www.intel.com}{Intel}.}\\ 
                & {\bf Member of the Computer Engineering Council at National} \\
				& {\bf University of C\'ordoba.}\\ \\
  {\bf Past}& 	{\bf Software Engineer at \href{http://www.nimbuzz.com/en/about}{Nimbuzz}.}\\
			& 	{\bf Software Engineer at Motorola Argentina}\\
			& 	$\triangleright$ Development of embedded software in C/C++ for Cable Modem products.\\
			&	$\triangleright$ Test Development and execution for the Motorola \href{http://www.motorola.com/web/Business/_Documents/White%20Paper/_Static%20files/NBBS%20WiMAX%20White%20Paper%20557127-001-b.pdf}{NBBS platform}.\\
			&	$\triangleright$ Development and maintenance of \href{http://en.wikipedia.org/wiki/Advanced_Telecommunications_Computing_Architecture}{AdvancedTCA} clusters running Linux.\\
			& 	{\bf Self-employed in Software Development and Maintenance}\\
			&	Since 2007. I worked in projects involving the optimization of scientific\\
			&	applications in multiprocessor systems.\\
			& 	{\bf Computer Architecture Laboratory, UNC}\\
			& 	Research Internship, From March/2006 to October/2007.\\
			& 	$\triangleright$ Optimization of Scientific programs over multiprocessor architectures and\\
			& 	parallel programming with MPI, HPF and OpenMP.\\
			& 	$\triangleright$ Testing of embedded systems for the biomedical industry.\\
			& 	{\bf Testing of the JOP processor and JDK}\\
			& 	I worked during 2007 for Martin Schoeberl from Viena University of\\
			&	Technology,	Austria.\\
			& 	{\bf Low level optimization of scientific programs}\\
			& 	I worked for Gerardo Hillman from the Hydric Resources Laboratory of the\\
			& 	National University of Cordoba at Argentina.\\
				
\end{tabular} 
\newpage
{\bf Publications} \\*[-.8pc]
\underline{\hspace{6in}} \\
$\triangleright$ Using JOP to build a chip multiprocessor JVM for embedded realtime systems. Annals of CACIC, 2007.\\
%$\triangleright$ Optimization of a bidimensional hydrodynamic model. ENIEF, 2009.\\
$\triangleright$ Optimization of an hydrodynamical bidimensional model. \href{http://www.cimec.org.ar/ojs/index.php/mc/article/viewFile/2930/2867}{link}. \\


{\bf Honors and Awards} \\*[-.8pc]
\underline{\hspace{6in}} \\
%\begin{itemize}
%\renewcommand{\labelitemi}{$\star$}
%\item
$\triangleright$ Grant earned for the completion of the Thesis Project.
Given by the Science Agency of C\'ordoba, 2006.\\ 
%\item
$\triangleright$ Distinction to the best average grade.
Given by the College of Engineering of C\'ordoba, 2007.\\
%\end{itemize}
\newline
{\large \bf Languages} \\*[-.8pc]
\underline{\hspace{6in}} \\
{\bf Spanish}\\
$\triangleright$ Native Spanish speaker.
\\
{\bf German}\\
$\triangleright$ Currently attending the third year of a four year course in German 
at the School of Languages of the National University of C\'ordoba.
 \\
{
{\bf English}\\
$\triangleright$ TOEFL iBT. Outcome 110 out of 120, March 2008.\\
$\triangleright$ First Certificate Examination grade B. Given by Cambridge University, 2000.\\
$\triangleright$ Several courses attended from 1992 to 2000.\\
{\bf Italian}\\
$\triangleright$ Four years course at the School of Languages of the National University of C\'ordoba, 2008.
\\
{\bf French}\\
$\triangleright$ One year course at "Alliance Fran\c caise C\'ordoba", 2000.
\\

{\large \bf Teaching Experience} \\*[-.8pc]
\underline{\hspace{6in}} \\
{\bf Concurrent Programming}\\
Computer engineering faculty, 2004.
\\
{\bf Calculus Tutor}\\
Electronic and Computer engineering faculty, 2003.
\\

{\large \bf Conferences attended as a lecturer} \\*[-.8pc]
\underline{\hspace{6in}} \\
{\bf  ENIEF, Congress on Numerical Methods and their Applications, 2009.}\\
Title: Optimization of an hydrodynamical bidimensional model. 
\\
{\bf  Second Open Conferences in Computer Engineering, National University of C\'ordoba.}\\
Title: Parallel Programming.
\\
{\bf  First Open Conferences in Computer Engineering, National University of C\'ordoba.}\\
Title: A multiprocessor JVM based on JOP.
\\
{{\bf  XIII Argentinian Congress on Computer Science}\\
Article's Title: Using JOP to build a chip multiprocessor JVM for embedded real-time systems.}\\
\newpage
{\large \bf Hobbies} \\*[-.8pc]
\underline{\hspace{6in}} \\
$\triangleright$ Trekking.\\
$\triangleright$ Amateur Guitar Player.\\
$\triangleright$ Cooking and beer brewing.\\
\end{document}




